A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-11-08 doc/large_strain.tex
add switch between IJNME and CMAME, enable CMAME for now

\RequirePackage[l2tabu, orthodox]{nag}
%\documentclass[12pt]{article}
% \documentclass[preprint,12pt,times]{elsarticle}
\documentclass[times,doublespace]{nmeauth}

%%% ELSOPTIONS:
% \biboptions{sort&compress,comma,square}
% \usepackage{amsmath}

%%%

@@

\runningheads{D. Davydov et al.}{A matrix-free approach for finite-strain hyperelastic problems}

@@

  \author{
    Denis Davydov\affil{1} \corrauth ,
    Jean-Paul Pelteret\affil{1},
    Daniel Arndt\affil{2},
    Paul Steinmann\affil{1,3}
  }

@@

  % \author[a]{Denis Davydov\corref{cor}}
  % \ead{denis.davydov@fau.de}

  % \author[a]{Jean-Paul Pelteret}
  % \ead{jean-paul.pelteret@fau.de}

  % \author[b]{Daniel Arndt}
  % \ead{daniel.arndt@iwr.uni-heidelberg.de}

  % \author[a,c]{Paul Steinmann}
  % \ead{paul.steinmann@fau.de}

  % \cortext[cor]{Corresponding author.}

  % \address[a]{Chair of Applied Mechanics,
  % Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  % Egerlandstr.\ 5, 91058 Erlangen, Germany}

  % \address[b]{Interdisciplinary Center for Scientific Computing (IWR),
  %     Heidelberg University,
  %     Im Neuenheimer Feld 205,
  %     69120 Heidelberg,
  %     Germany}

  % \address[c]{Glasgow Computational Engineering Center (GCEC),
  %     University of Glasgow, G12 8QQ Glasgow, United Kingdom
  % }

@@

  \keywords{
  % \begin{keyword}
      adaptive finite element method ; %\sep
      geometric multigrid ; %\sep
      finite-strain ; %\sep
      matrix-free ; %\sep
      hyperelasticity
  % \end{keyword}
  }

  \maketitle
  % \end{frontmatter}

@@

\acks
% \section*{Acknowledgements}

@@

% \section*{Bibliography}

\bibliographystyle{wileyj}
% \bibliographystyle{elsarticle-num}

>>>>

\RequirePackage[l2tabu, orthodox]{nag}

\newif\ifijnme %Declaration of ijnme
% \ijnmetrue %Sets ijnme to true
\ijnmefalse %Sets ijnme to false

\ifijnme
\documentclass[times,doublespace]{nmeauth}
\else
\documentclass[preprint,12pt,times]{elsarticle}
\biboptions{sort&compress,comma,square}
\usepackage{amsmath}
\fi

@@

\ifijnme
\runningheads{D. Davydov et al.}{A matrix-free approach for finite-strain hyperelastic problems}
\else
\journal{CMAME}
\begin{frontmatter}
\fi

@@

\ifijnme
  \author{
    Denis Davydov\affil{1} \corrauth ,
    Jean-Paul Pelteret\affil{1},
    Daniel Arndt\affil{2},
    Paul Steinmann\affil{1,3}
  }

@@

\else
  \author[a]{Denis Davydov\corref{cor}}
  \ead{denis.davydov@fau.de}

  \author[a]{Jean-Paul Pelteret}
  \ead{jean-paul.pelteret@fau.de}

  \author[b]{Daniel Arndt}
  \ead{daniel.arndt@iwr.uni-heidelberg.de}

  \author[a,c]{Paul Steinmann}
  \ead{paul.steinmann@fau.de}

  \cortext[cor]{Corresponding author.}

  \address[a]{Chair of Applied Mechanics,
  Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  Egerlandstr.\ 5, 91058 Erlangen, Germany}

  \address[b]{Interdisciplinary Center for Scientific Computing (IWR),
      Heidelberg University,
      Im Neuenheimer Feld 205,
      69120 Heidelberg,
      Germany}

  \address[c]{Glasgow Computational Engineering Center (GCEC),
      University of Glasgow, G12 8QQ Glasgow, United Kingdom
  }
\fi

@@

\ifijnme

  \keywords{
      adaptive finite element method ;
      geometric multigrid ;
      finite-strain ;
      matrix-free ;
      hyperelasticity
  }

  \maketitle

\else
    \begin{keyword}
        adaptive finite element method \sep
        geometric multigrid \sep
        finite-strain \sep
        matrix-free \sep
        hyperelasticity
    \end{keyword}

\end{frontmatter}
\fi

@@

\ifijnme
\acks
\else
\section*{Acknowledgements}
\fi

@@

\ifijnme
\bibliographystyle{wileyj}
\else
\section*{Bibliography}
\bibliographystyle{elsarticle-num}
\fi
